Functions Created

### 2017-08-10 Hours.Rmd
set up a CR model similar to one described in literature review, compared results
finished comparing results to stack overflow model, continued with model fitting, added interactions, updated hours
copied data file folder
updated hours, organized files

>>>>

8/4/2017 | 5.5 | 3:00-8:30PM | Fit a model similar to one found in literature reviews, compared results
8/7/2017 | 4.5 | 11:00-3:30PM | Continued with comparing model results to Stack overflow. 
8/7/2017 | 3 | 5:45-8:45 | Used AIC, fit model 
8/8/2017 | 2.5 | 9:30-12:00PM | Model fitting research
8/8/2017 | 3 | 1:00-4:00PM | Worked with Anthony on building an R package 
8/9/2017 | 4.25 | 10:45-3:00PM | Predictive model fitting research, reviewed cox regression notes from STAT 417
8/9/2017 | 3 | 9:30-12:30AM | Found predictive model article, researched terminology from the article, found r packages to use
8/10/2017 | | 8:00- | Finished putting functions in r package, organized files, continued with model fitting research
